CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-09-28 codecheck-paper.tex
add remaining checks to the table

  \begin{tabular}{llp{11cm}}
    \toprule
    Certificate & Research area & Description \\ \midrule
    2020-001 \cite{cert-2020-001} &
    Machine learning & CODECHECK undertaken post acceptance of
    manuscript and before its publication in \textit{Gigascience}
    \cite{Piccolo2020-lo}.
    \\
    2020-002  \cite{cert-2020-002} & neuroscience & Paper from 1997
 showing unsupervised learning from natural images \cite{Hancock1992-mp}.
 Code written for this project.
    \\
    2020-003  \cite{cert-2020-003} & neuroscience &
                                                     Classic paper
                                                     from 1982 on
                                                     models of
                                                     associative
                                                     memory
                                                     \cite{Hopfield1982-mz}.
    (Simulation code was written specifically for this project.)\\
    2020-004  \cite{cert-2020-004} & area & Cart-pole balancing problem solved using reinforcement learning \cite{Barto1983-rg}.  Code written for this reimplementation.\\
    2020-005  \cite{cert-2020-005} & area & Larisch \\
    2020-006  \cite{cert-2020-006} & area & Detorakis \\
    2020-007  \cite{cert-2020-007} & area & in progress \\
    2020-008  \cite{cert-2020-008} & Covid & Modelling of
    interventions on Covid  cases in the UK; checked as preprint (NOW REMOVED XXX)
    and now published \cite{Davies2020-vj} \\
    2020-009  \cite{cert-2020-009} & Covid &  tracing \\
    2020-010  \cite{cert-2020-010} & Covid &  report 9 \\
    2020-011  \cite{cert-2020-011} & Covid & Modelling of Covid
    spread across Europe;  paper was checked when in press (now  published) \cite{Flaxman2020-yb}. \\
    2020-012  \cite{cert-2020-012} & Covid &   Modelling of Covid spread across the USA; preprint currently review \cite{Unwin2020}. \\
    \\ \bottomrule
  \end{tabular}
  \caption{Register of completed certificates.  An interactive version
  of this is available at \url{http://codecheck.org.uk/register}.  SJE
to complete...}
  \label{tab:register}
\end{table}

>>>>

  \begin{tabular}{llp{11cm}}
    \toprule
    Certificate & Research area & Description \\ \midrule
    2020-001 \cite{cert-2020-001} &
    Machine learning & CODECHECK undertaken post acceptance of
    manuscript and before its publication in \textit{Gigascience}
    \cite{Piccolo2020-lo}.
    \\
    2020-002  \cite{cert-2020-002} & neuroscience & Paper from 1997
 showing unsupervised learning from natural images \cite{Hancock1992-mp}.
 Code written for this project.
    \\
    2020-003  \cite{cert-2020-003} & neuroscience &
                                                     Classic paper
                                                     from 1982 on
                                                     models of
                                                     associative
                                                     memory
                                                     \cite{Hopfield1982-mz}.
    (Simulation code was written specifically for this project.)\\
    2020-004  \cite{cert-2020-004} & area & Cart-pole balancing problem solved using reinforcement learning \cite{Barto1983-rg}.  Code written for this reimplementation.\\
    2020-005  \cite{cert-2020-005} & area & Larisch \\
    2020-006  \cite{cert-2020-006} & area & Detorakis \\
    2020-007  \cite{cert-2020-007} & area & in progress \\
    2020-008  \cite{cert-2020-008} & Covid & Modelling of
    interventions on Covid  cases in the UK; checked as preprint (NOW REMOVED XXX)
    and now published \cite{Davies2020-vj} \\
    2020-009  \cite{cert-2020-009} & Covid &  tracing \\
    2020-010  \cite{cert-2020-010} & Covid &  report 9 \\
    2020-011  \cite{cert-2020-011} & Covid & Modelling of Covid
    spread across Europe;  paper was checked when in press (now  published) \cite{Flaxman2020-yb}. \\
    2020-012  \cite{cert-2020-012} & Covid &   Modelling of Covid spread across the USA; preprint currently review \cite{Unwin2020}. \\
    2020-013  \cite{cert-2020-013} & area & biorXiv \cite{Spitschan2020.06.02.129502}. \\
    2020-014  \cite{cert-2020-014} & area & eLife \cite{Sadeh2020}. \\
    2020-015  \cite{cert-2020-015} & area & eLife \cite{Liou2020}. \\
    2020-016  \cite{cert-2020-016} & GIScience & 
    R models demonstrating the Modifiable Aral Unit Problem (MAUP) in spatial data science \cite{Brunsdon2020}. \\
    2020-017  \cite{cert-2020-017} & GIScience & 
    Spatial data handling, analysis, and visualisation using a variety of R packages \cite{Bivand2020}. \\
    2020-018  \cite{cert-2020-018} & GIScience & 
    Cellular automaton in R for modeling dynamic phenomena within a Discrete Global Grid System (DGGS) data model; using a subset for demonstration \cite{Hojati2020}. \\
    2020-019  \cite{cert-2020-019} & GIScience & Reachability analysis of suburban transportation using analysis of privately owned shared cars; workflow uses Python, and reproduction with a considerably subsampled dataset \cite{Illium2020}. \\
    2020-020  \cite{cert-2020-020} & GIScience & In-database windows operators for processing spatio-temporal data streams based on Python and PostgreSQL/PostGIS \cite{Werner2020}; reproduction using container. \\
    2020-021  \cite{cert-2020-021} & GIScience & Python code for comparing supervised machine learning models for spatial nominal entity recognition. \cite{Medad2020}. \\
    2020-022  \cite{cert-2020-022} & GIScience & Python code for visualising text analysis on intents and concepts from geo-analytic questions \cite{Xu2020}. \\
    2020-023  \cite{cert-2020-023} & GIScience & Analysis of spatial footprints of geo-tagged extreme weather events from social media using R \cite{Owuor2020}. \\
    \\ \bottomrule
  \end{tabular}
  \caption{Register of completed certificates as of October 2020.  An interactive version
  of this is available at \url{http://codecheck.org.uk/register}.  SJE
to complete...}
  \label{tab:register}
\end{table}
